The advancement of technology and the increase in the use of the Internet increases the amount of information on the Web. The expansion of smartphones and social networks provides a great production of data. In the presence of this information, it is not always possible to differentiate what is useful, and there is the need to filter what is necessary or not. Recommendation Systems comes as one of the resolutions to this problem. Through user data and items, the system has the ability to recommend items according to the tastes of a particular user.

In tourism there is the same event. Usually the tourist has problems to build an itinerary so that he can visit tourist spots matching his preferences. In this sense, this work aims to optimize the use of geographic location to recommend tourist spots in tourism apps. This project presents a recommendation system that suggests a route with the most relevant tourist points to the user, according to their interests. The recommendations are based on ratings from other users about Salvador. Technically, the recommendation models use methods based on in the similarity between the items and based on the content of the points of interest

The results show that it is possible to make recommendations of sights, considering the options of the user. Precision and Recall metrics improved approximately 75\% and 90\%, respectively, between the two recommendation models used in this project. This work can be considered the beginning of the resolution of a problem that is frequent to several tourists in front of a great amount of options of points of interest.

\begin{keywords}
Recommendation Systems, Tourism, Routes, Location
\end{keywords}